PDBF Documentation

### 2015-05-27 Documentation.tex
added some notes to config. changed documentclass of minimal example.

\section{Requirements}
These \LaTeX\relax packages are required for PDBF documents:\\
zref-savepos\\
zref-abspage\\
zref-user\\
xcolor\\
graphicx\\
xstring\\
xparse\\
geometry\\

>>>>

\section{Requirements}
These \LaTeX\relax packages are required for PDBF documents:\\
zref\\
xcolor\\
graphicx\\
xstring\\
xparse\\
geometry\\
